Ceph Parallel File System Evaluation Report

### 2013-08-28 ceph-initial.tex
changes here and there, again

We used the synthetic IOR benchmark suite for file system level performance
and scalability test.  The particular parameter setup is show in Table
\ref{tbl:ior}. Each client node has 6 GB of physical memory, the block size is
set so as to mitigate cache effects. In addition, the test harness program
issues the following commands at the beginning of each test:

@@

In our particular setup, we only had one metadata server (MDS) configured.
Therefore, this is not a scalability test on the performance of Ceph clustered
MDS, which would have been very interesting.  Instead, we focus on a single MDS
performance and exercise it with up to 8 clients to observe the single MDS
performance scaling. We used mdtest as our benchmark tool. Mdtest parameters
used for this test are:

>>>>

We used the synthetic IOR benchmark
suite\footnote{\url{http://sourceforge.net/projects/ior-sio/}} for file system
level performance and scalability test.  The particular parameter setup is show
in Table \ref{tbl:ior}. Each client node has 6 GB of physical memory, the block
size is set so as to mitigate cache effects. In addition, the test harness
program issues the following commands at the beginning of each test:

@@

In our particular setup, we only had one metadata server (MDS) configured.
Therefore, this is not a scalability test on the performance of Ceph clustered
MDS, which would have been very interesting.  Instead, we focus on a single MDS
performance and exercise it with up to 8 clients to observe the single MDS
performance scaling. We used
mdtest\footnote{\url{http://sourceforge.net/projects/mdtest/}} as our benchmark
tool. Mdtest parameters used for this test are:

### 2013-08-28 ceph-tuning.tex
changes here and there, again

We now repeated the previous RADOS scaling tests with these improvements in place.
The first test was done on a single node with RADOS Bench to see how close the
underlying object store could get to the node hardware limitations as the number
of OSDs/LUNs used on the node increased. Note all the tests performed were against
XFS-formatted storage.

@@

\begin{figure}[htb]
\centering
\includegraphics[width=3.5in]{rados-064-osd}
\caption{RADOS Bench Scaling on \# of OSD, Ceph 0.64, 4 MB I/O, 8 Client Nodes}
\label{fig:rados-064-osd}
\end{figure}

In the single server case as shown in Figure~\ref{fig:rados-064-osd}, ``Writes
(including Journals)'' refers to how much data is actually being written out the
DDN chasis, and blue line is how much data the clients are writing.
We observe that performance gets very close to the hardware limits at roughly 9
OSDs per server and then mostly levels out.

@@

At this point, we were able to both make more client nodes available for Ceph
file system-level testing and also install a profiling tool called \verb!perf!
that is extremely useful for profiling both kernel and user space codes.
Profiling with \verb!perf! showed high CPU utilization on test clients due to
crc32c processing in the Ceph kernel client.  crc32 checksums can be disabled
by changing the CephFS mount options:

@@

Deeper analysis with perf showed that there was heavy lock contention during
parallel compaction in the Linux kernel memory manager.  This behavior was first
observed roughly in the kernel 3.5 time frame which was the kernel
installed on our test systems.\footnote{For more information,
please refer to \url{http://lwn.net/Articles/517082/} and
\url{https://patchwork.kernel.org/patch/1338691/}.}

@@

As can be seen, with the 3.9 kernel, while there was a slight improvement on
write performance, read performance improved dramatically.  In addition to the
kernel change, Sage Weil from InkTank suggested increasing the amount of CephFS
client kernel read-ahead cache size as:

@@

By installing a newer kernel, increasing read-ahead cache size, and increasing the number of
client IOR processes, we were able to achieve very satisfactory I/O performance.

@@

As before, we ran IOR scaling tests with two cases: transfer size 4 KB and 4 MB.
These results are illustrated in Figure~\ref{fig:ior-064}. As expected, we saw
saw  improved read and write performance. These new read and write performance are in
line with observed RADOS bench performance.

@@

Throughout our IOR testing, we observed that the average write throughput is 
lower than the maximum.  This behavior was observed during other tests as well,
indicating that we may have periods of time where write throughput is
temporarily degrading.  Despite these issues, performance generally seems to be
improving with respect to increasing number of clients.  Writes seem to be topping out at
around 5.2 GB/s (which is roughly what we would expect).  Reads seem to be
topping out anywhere from 5.6-7 GB/s, however it is unclear if read performance
would continue scaling with more clients and get closer to ~8 GB/s  we
obervered with RADOS Bench.

\subsection{Revisit Metadata Performance}

Our previous results show that file creation rate is significantly lower than
directory creation rate. Also, we conjectured two reasons: one is the file
creation is associated with 1 MB data write and followed by a fsync operation.
Another reason being that we obtained above results from early version of Ceph
without all the tunings and improvement applied.

>>>>

We now repeated the previous RADOS scaling tests with these improvements in place.
The first test was done on a single node with RADOS Bench to see how close the
underlying object store could get to the node hardware limitations as the number
of OSDs/LUNs used on the node increased. All the tests performed were against
XFS-formatted storage.

@@

\begin{figure}[htb]
\centering
\includegraphics[width=3.5in]{rados-064-osd}
\caption{RADOS Bench Scaling on number of OSD, Ceph 0.64, 4 MB I/O, 8 Client Nodes}
\label{fig:rados-064-osd}
\end{figure}

In the single server case as shown in Figure~\ref{fig:rados-064-osd}, ``Writes
(including Journals)'' refers to how much data is actually being written out
the DDN SFA10K (observed directly from the controllers), and blue line is how
much data the clients are writing.  We observe that performance observed by the
DDN controllers gets very close to the hardware limits at roughly 9 OSDs per
server and then mostly levels out.

@@

At this point, we were able to both make more client nodes available for Ceph
file system-level testing and also install a profiling tool called \verb!perf!
that is extremely useful for profiling both kernel and user space codes.
Profiling with \verb!perf! showed high CPU utilization on test clients due to
CRC32c processing in the Ceph kernel client.  CRC32 checksums can be disabled
by changing the CephFS mount options:

@@

Deeper analysis with \verb!perf! showed that there was heavy lock contention during
parallel compaction in the Linux kernel memory manager.  This behavior was first
observed roughly in the kernel 3.5 time frame which was the kernel
installed on our test systems.\footnote{For more information,
please refer to \url{http://lwn.net/Articles/517082/} and
\url{https://patchwork.kernel.org/patch/1338691/}.}

@@

As can be seen, with the 3.9 kernel, while there was a slight improvement on
write performance, read performance improved dramatically.  In addition to the
kernel change, the amount of CephFS
client kernel read-ahead cache size was improved as:

@@

By installing a newer kernel, increasing read-ahead cache size, and increasing
the number of client IOR processes, we were able to achieve very satisfactory
I/O performance at the Ceph file system-level.

@@

As before, we ran IOR scaling tests with two cases: transfer size 4 KB and 4
MB.  These results are illustrated in Figure~\ref{fig:ior-064}, respectively.
As expected, we saw saw  improved read and write performance. These new read
and write performance are in line with observed RADOS bench performance.

@@

Throughout our IOR testing, we observed that the average write throughput is
lower than the maximum.  This behavior was observed during other tests as well,
indicating that we may have periods of time where write throughput is
temporarily degrading.  Despite these issues, performance generally seems to be
improving with respect to increasing number of clients.  Writes seem to be
topping out at around 5.2 GB/s (which is roughly what we would expect due to
journalling effectively halving the write performance).  Reads seem to be
topping out anywhere from 5.6-7 GB/s, however it is unclear if read performance
would continue scaling with more clients and get closer to ~8 GB/s we observed 
with RADOS Bench.

\subsection{Revisiting Metadata Performance}

Our previous results show that file creation rate is significantly lower than
directory creation rate. Also, we conjectured two reasons: one is the file
creation is associated with 1 MB data write and followed by a \verb!fsync!
operation.  Another reason being that we obtained above results from early
version of Ceph without all the tunings and improvement applied.

### 2013-08-28 conclusion.tex
add paper flow and organization into introduction
changes here and there, again

\section{Observations and Conclusions}

@@

  \item Ceph performs \textbf{metadata + data} journaling, which is fine for
host systems that has locally attached disk. However, this presents a problem
in DDN SFA10K-like hardware, where the backend LUNs are exposed as block
devices through SCSI Request Protocol (SRP) over IB. The journaling write
requires twice the bandwidth compare to Lustre-like metadata-only journaling
mechanism. For Ceph to be viable in this facility, journaling operations will
need to further design and engineering.

>>>>

\section{Observations and Conclusions}
\label{sec:conclusion}

@@

  \item Ceph performs \textbf{metadata + data} journaling, which is fine for
host systems that has locally attached disk. However, this presents a problem
in DDN SFA10K-like hardware, where the backend LUNs are exposed as block
devices through IB over SRP protocol. The journaling write requires twice the
bandwidth compared to Lustre-like meta data-only journaling mechanism. For Ceph
to be viable in large-scale capability HPC environments like ours, journaling
operations will need to further design and engineering.
